### 2020-08-11 text/article_vedrovice.Rmd
text - introduction

@@

@@

@@

@@

```{r gabriel, fig.cap = "Gabriel graph"}
knitr::include_graphics(here("plots", "plan_vedrovice_gabriel.pdf"))
```

@@

@@

```{r label-neigh_sex}
label_neigh_sex <- paste("Mean neighbors in a given sex category",
"*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value.",
"*F* -- female, *M* -- male, *n. a.* -- non adult.")
```
```{r neigh-sex, fig.cap = label_neigh_sex}
knitr::include_graphics(here("plots", "prob_neighbour_sex.pdf"))
```

>>>>

The Cemetery of Vedrovice is one of the earliest and most extensively studied
cemeteries of the *Linearbandkeramik* (LBK).
Recent contributions use the evidence from the cemetery in a broader discussion
of post-marital residence patterns [@hrncir2020] and
sexual inequalities and gender in the Neolithic [@masclanslatorre2020; @bickle2020].
Here we focus on detailed analysis of the distribution of the grave goods and
spatial analysis of the Vedrovice cemetery in respect to gender relations.

<!-- gender relations -->

<!-- view of gender in the Neolithic, archaeological context -->
@robb2017 [128] noted lack of gender archaeology debate for the
European Neolithic in comparison with other periods, especially the Bronze Age.
They argue that a the perception of gender in the Neolithic and the Bronze Age is
not the same (ibid. 142).
In response, @bickle2020 [14] shows that 'biological sex may not have defined gender
during the LBK' although the 'sexed bodies did matter'.

<!-- resampling and computer-intensive techniques-->
The approach taken is a quantitative one embracing resampling techniques and
computer-intensive methods in general.
The resampling techniques were introduced to mortuary studies by
@manly1996 but the application is still limited [@sosna2008, 343].
As noted by Sosna (ibid.), the most important benefit of resampling is in its
ability to distinguish random and non-random patterns.

@@

<!-- site -->

<!-- sample (burials, artefacts) -->

@@

<!-- methods -->

<!-- spatial analysis -->

@@

<!-- software packages -->

@@

```{r gabriel, fig.cap = "Gabriel graph"}
knitr::include_graphics(here("plots", "plan_gabriel.pdf"))
```

@@

<!-- results -->

@@

```{r label-nb}
label_neigh_sex <- paste("Mean neighbors in a given sex category",
"*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value.",
"*F* -- female, *M* -- male, *n. a.* -- non adult.")
```
```{r nb-buffer, fig.cap = label_neigh_sex}
knitr::include_graphics(here("plots", "nb_buffer_sex.pdf"))
```
```{r nb-gabriel, fig.cap = label_neigh_sex}
knitr::include_graphics(here("plots", "nb_gabriel_sex.pdf"))
```
